Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-28 WSSSPE2_report/WSSSPE2_review.tex
BIb and Section 4: Simplified.

\subsection{Samin Ishtiaq: Daemons, Notifications and Sustaining Software~\cite{Ishtiaq_poster}}
%  Microsoft Research Cambridge
The reproduction and replication of novel results has become a major issue in
computer science, systems biology, and other computational disciplines. These
include both the inability to re-implement novel algorithms and approaches, and
lack of an agreement on how and what to benchmark these algorithms on.
Ishtiaq from Microsoft Research Cambridge pointed out these problems and 
made several suggestions to address them.

\subsection{James Howison: Retract all Bit-Rotten Publications~\cite{Howison_poster}}
Howison sought to provoke discussion by proposing that papers whose workflows are
not kept current with the changing software ecosystem should be automatically
retracted. This would create an incentive for authors to keep their
software current and usable, rather than the current situation in which every
potential user has to do this individually. A softer version of the proposal
would identify papers whose software workflow has become bit-rotten and allow
others to keep the code up to date, either adding them as new authors of the
paper or providing credit in some other form for their academic service.

@@

\subsection{Alice Allen: Find it! Cite it!~\cite{Allen_poster}}
%
The Astrophysics Source Code Library (ASCL) is an online registry of
scientist-written software used in astronomy research. Their primary interest is
rendering research more transparent by making this software more discoverable for
examination. The ASCL is treated as a publication by an indexing resource for
astronomy, the Astrophysics Data System (ADS). ADS tracks citations to what it
indexes, including citations to ASCL entries. Increasing rewards for writing
software, whether through citation, transitive credit or other methods, gives
software authors a powerful reason to take the time to build sustainability into
their software and is an excellent way to drive community change.

>>>>

\subsection{Samin Ishtiaq: Daemons, Notifications and Sustaining Software}%~\cite{Ishtiaq_poster}}
%  Microsoft Research Cambridge
The reproduction and replication of novel results has become a major issue in
computer science, systems biology, and other computational disciplines. These
include both the inability to re-implement novel algorithms and approaches, and
lack of an agreement on how and what to benchmark these algorithms on.
Ishtiaq from Microsoft Research Cambridge pointed out these problems and 
made several suggestions to address them.

\subsection{James Howison: Retract all Bit-Rotten Publications}%~\cite{Howison_poster}}
Howison sought to provoke discussion by proposing that papers whose workflows are
not kept current with the changing software ecosystem should be automatically
retracted. This would create an incentive for authors to keep their
software current and usable, rather than the current situation in which every
potential user has to do this individually. A softer version of the proposal
would identify papers whose software workflow has become bit-rotten and allow
others to keep the code up to date, either adding them as new authors of the
paper or providing credit in some other form for their academic service.

@@

\subsection{Alice Allen: Find it! Cite it!}%~\cite{Allen_poster}}
%
The Astrophysics Source Code Library (ASCL) is an online registry of
scientist-written software used in astronomy research. Their primary interest is
rendering research more transparent by making this software more discoverable for
examination. The ASCL is treated as a publication by an indexing resource for
astronomy, the Astrophysics Data System (ADS). ADS tracks citations to what it
indexes, including citations to ASCL entries. Increasing rewards for writing
software, whether through citation, transitive credit or other methods, gives
software authors a powerful reason to take the time to build sustainability into
their software and is an excellent way to drive community change.
